NoTitle

### 2017-06-12 Aplas17/sections/Overview.tex
Some Text for Overview

\section{A Running Example: DrawableDeck}~\label{sec:overview}
\includegraphics[height=3.3cm]{pics/DrawableLoggingDeck.pdf}
\red{H: with UML graphs the illustration could be better.}
This section illustrates the features of our \MIM{} model for resolving unintentional method
conflicts. As mentioned before, such a case arises when two inherited methods happen to have the
same signature, but with different semantics and functionalities. This could be quite troublesome
to programmers that use multiple inheritance. Below we illustrate with a running example called \lstinline|DrawableDeck|.
Note that we use Java-like syntax throughout the paper, and all types are defined with the keyword ``\lstinline|interface|''. The concept
is closely related to Java 8 interfaces, and traits. For simplicity, an interface in our model has the following characteristics:
\begin{itemize}
	\item It allows multiple inheritance.
	\item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There is no abstract method.
	\item It can be directly instantiated by the \lstinline|new| keyword.
\end{itemize}
Furthermore for simplicity, our formalization does not model state at this stage, but that should not block our discussions below.

@@

Suppose that two components \lstinline|Deck| and \lstinline|Drawable| have been developed in a system.
\lstinline|Deck| represents a deck of cards, and defines \lstinline|draw()| for drawing a card from the deck.
While \lstinline|Drawable| is an interface for graphics that can be drawn, and also includes a method called \lstinline|draw()|
for visual display. For illustration, the implementation of \lstinline|draw()| in \lstinline|Drawable|
only creates a blank canvas on the screen, and later some instances (\lstinline|Circle|, \lstinline|Square|, or whatever) that extend
\lstinline|Drawable| may define their own \lstinline|drawObject()| methods and invoke \lstinline|draw()|.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(true);
    ...
  }
}
\end{lstlisting}\vspace{3pt}
Note that both methods have \lstinline|void| return type (we will not formalize
\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

\vspace{3pt}\begin{lstlisting}
interface DrawableDeck extends Drawable, Deck {...} 
\end{lstlisting}\vspace{3pt}
The point of using multiple inheritance is surely for composing the features of
components, achieving great code reuse. It is supported by many mainstream OO
languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
error, for the two \lstinline|draw()| methods cause a conflict, though accidentally.

@@

For that problem, there are several workarounds that quickly come to our mind:

\paragraph{I. Delegation.} As an alternative to multiple inheritance, delegation can be used by
introducing two fields with \lstinline|Drawable| type and \lstinline|Deck| type, respectively. This avoids
method conflicts. Nevertheless, it is known that using delegation makes it hard to correctly maintain self-references \haoyuan{?} in an
extensible system [], and meanwhile introduces a lot of boilerplate.

@@

\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.

>>>>

\section{A Running Example: DrawableDeck}~\label{sec:overview}
\includegraphics[height=3.3cm]{pics/DrawableLoggingDeck.pdf}
\red{H: with UML graphs the illustration could be better.}

This section illustrates the features of our \MIM{} model for
resolving unintentional method conflicts. As mentioned before, such a
case arises when two inherited methods happen to have the same
signature, but with different semantics and functionality. This
situation is troublesome to programmers that use multiple
inheritance. Below we illustrate with a running example called
\lstinline|DrawableDeck|, which models a drawable deck of cards. 
Note that we use Java-like syntax
throughout the paper, and all types are defined with the keyword
``\lstinline|interface|''. The concept is closely related to Java 8
interfaces, and traits. For simplicity, an interface in our model has
the following characteristics:
\begin{itemize}
	\item It allows multiple inheritance.
	\item Every method represents a behaviour and requires a body for its implementation (like Java 8 default methods). There are no abstract methods.
	\item It can be directly instantiated by the \lstinline|new| keyword.
\end{itemize}
Furthermore for simplicity, our formalization does not model state at
this stage. %%, but that should not block our discussions below.

@@

Suppose that two components \lstinline|Deck| and \lstinline|Drawable| 
have been developed in a system.  \lstinline|Deck| represents a deck
of cards, and defines \lstinline|draw()| for drawing a card from the
deck.  While \lstinline|Drawable| is an interface for graphics that
can be drawn, and also includes a method called \lstinline|draw()| for
visual display. For illustration, the implementation of
\lstinline|draw()| in \lstinline|Drawable| only creates a blank canvas
on the screen, and later some instances (\lstinline|Circle|,
\lstinline|Square|, or others) that extend \lstinline|Drawable| may
define their own \lstinline|drawObject()| methods and invoke
\lstinline|draw()|.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame("Canvas");
    frame.setVisible(true);
    ...
  }
}
\end{lstlisting}\vspace{3pt}
\bruno{Space is probably going to be a problem, so you may have to
  consider putting code side-by-side to maximize space usage.}
Note that both methods have \lstinline|void| return type (we will not formalize
\lstinline|void| in our calculus afterwards; here is only for illustration). In \lstinline|Deck|, \lstinline|draw()| tries to get the cards as a stack, pops
out the top card, and so on. While in \lstinline|Drawable|, \lstinline|draw()|
creates a blank canvas using \lstinline|JFrame|. Now, a programmer is designing a
card game with GUI. He may want to draw a deck on the screen, so he defines a drawable
deck using multiple inheritance:

\vspace{3pt}\begin{lstlisting}
interface DrawableDeck extends Drawable, Deck {...} 
\end{lstlisting}\vspace{3pt}
The point of using multiple inheritance is surely for composing the features from
components, and to achieve code reuse. Multiple inheritance is supported by many mainstream OO
languages. Nevertheless at this point, \lstinline|DrawableDeck| has to throw a compile
error, since the two \lstinline|draw()| methods cause a conflict, though accidentally.

@@

For that problem, there are several workarounds. We go over some of
the main ones next.

\paragraph{I. Delegation.} As an alternative to multiple inheritance,
delegation can be used by introducing two fields with
\lstinline|Drawable| type and \lstinline|Deck| type,
respectively. This avoids method conflicts. Nevertheless, it is known
that using delegation makes it hard to correctly maintain
self-references \haoyuan{?} in an extensible system [], and also
introduces a lot of boilerplate code.

@@

\paragraph{III. Refactor Drawable and/or Deck to rename the methods.} If
the code for \lstinline|Drawable| or \lstinline|Deck| are available
then it may be possible to rename one of the \lstinline|draw|
methods. However this approach is non-modular, as it requires 
modifying existing code, and may not be possible if code is unavailable.

%\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
%default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.
